\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-30 manuscript/manuscript.tex
addressed the AE's comment

Developing a fully nonparametric solution for the KS
tests in the presence of serial dependence presents a significant
challenge. The null distribution's characteristics are intricately linked to
the structure of the serial dependence, which can vary widely in practical
situations. Employing a nonparametric method would necessitate defining a
specific model for this dependence, despite the primary focus being on
evaluating the marginal distribution of a stationary series. To date, a bias
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks
to bridge this gap by introducing a bias correction technique for the
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the
hypothesized distribution has unspecified parameters and the data
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

>>>>

Developing a fully nonparametric solution for the KS
tests in the presence of serial dependence presents a significant
challenge. The null distribution's characteristics are intricately linked to
the structure of the serial dependence, which can vary widely in practical
situations. Employing a parametric method would necessitate defining a
specific model for this dependence, despite the primary focus being on
evaluating the marginal distribution of a stationary series. To date, a bias
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks
to bridge this gap by introducing a bias correction technique for the
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the
hypothesized distribution has unspecified parameters and the data
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

### 2025-05-30 manuscript/reply.tex
addressed the AE's comment

Two reviewers have carefully read the paper and have provided detailed feedback.  Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the Babu and Rao (2004) paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).  A successful revision will require that the authors give serious consideration to these points.

I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
\end{comment}

@@

@@

@@

\begin{comment}
2. The work presented here is useful, however I have believe the explanations
for the correction term may need modification. Here the entire justification is
based on the null case which does not cover the case when the null is not true.
Justification for the correction term in \citet{babu2004goodness} is not based 
on just the
null case. The same seems to be true here, and in that case, Section 2 needs
rewriting.
\end{comment}

>>>>

Two reviewers have carefully read the paper and have provided detailed feedback.  Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the Babu and Rao (2004) paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).  A successful revision will require that the authors give serious consideration to these points.
\end{comment}

\begin{comment}
1. I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
\end{comment}

Thank you for pointing out this error in our manuscript. We have corrected
it from "nonparametric" to "parametric" accordingly.

@@

\begin{comment}
This manuscript proposes a nonparametric block bootstrap (NPBB) method for applying the
Kolmogorov-Smirnov (KS) test to stationary time series data with unknown parameters and unspecified serial dependence. The authors claim that the method offers a robust nonparametric solution for evaluating the fit of marginal distributions when data are serially dependent, without
requiring assumptions about the form of this dependence. The paper is well-written and smooth
to read. However, upon review, I find that it lacks methodological and theoretical innovation.
\end{comment}

@@

\begin{comment}
This paper focuses on approximating the distribution of the Kolmogorov-
Smirnov (KS) statistic for stationary time series. Specifically, it deals with the
distribution of KS statistic for testing if the marginal distribution belongs to
a specified parametric family. Parametric bootstrap requires knowledge of the
nature of serial dependence, and for this reason, nonparametric bootstrap is 
employed here. For the iid case, \citet{babu2004goodness} obtained a correction 
term so that the corrected bootstraped statistic can be used to approximate 
distribution of the KS statistic. This paper does the same except it uses 
nonparametric bootstrap developed by Kunsch and others. Finally the author(s) 
present some empirical work in support of their proposed procedure. Simulations 
indicate that the proposed procedure may work for large samples and moderate depen-
dence.
\end{comment}

@@

\begin{comment}
2. The work presented here is useful, however I have believe the explanations
for the correction term may need modification. Here the entire justification is
based on the null case which does not cover the case when the null is not true.
Justification for the correction term in \citet{babu2004goodness} is not based 
on just the
null case. The same seems to be true here, and in that case, Section 2 needs
rewriting.

Here is what I am able to understand after reading this paper, the papers
by Babu and Rao, and Kunsch and others.

Following the notations in this paper (the same notations have been used in
Babu and Rao), let

\mc{I will insert the rest of the comment here}
\end{comment}
